A Comparison of Use-Case Based and Checklist- Based Reading: A Controlled Experiment

### 2015-03-17 rmtw/a6/latex8.tex
Pushed initial layout for a6

\section{Introduction}
Statement of the problem and why it	is important

\subsection*{Problem Statement}
Include existing literature about the problem, 5-10 references required.

\subsection*{Purpose Statement}
Concise, clear

\section{Company Case Description}

\section{Methodology}
• State	your	research	question(s)	(and	hypothesis	if	applicable)
• Describe	and	explain	the	research	strategy	and	investigation	methods that	will	be	used	for	the	project.	Motivate	your	choice?
• Research	strategy	(research	methodology)
• data	collection	procedures	(e.g.	interviews?	survey?	and	sampling?)	
• method	for	analyzing	the	data	(grounded	theory?	Thematic	analysis?	
Statistical	analysis?)	strategies	for	validating	findings

>>>>

\section{Introduction}
%Literature intro
%A bit unclear what to write here - check with Branson

\subsection{Problem Statement}

\subsection{Purpose Statement}

\subsection{Research Questions}

\section{Related Work}

\subsection{API Design}

\subsection{Software Evolution}

\subsection{Architecture / Reverse Engineering (or tracing previously made decisions)}

\section{Case Company Description}
*Not sure if this should be a sub-heading somewhere

\section{Methodology}
Brief intro, saying we will do a case study and what data collection methods will be used. (Also citing the paper from where we steal the case study process... höst).

\subsection{Case Study Design}

\subsection{Preparation for Data Collection}

\subsection{Data Gathering}

\subsection{Data Analysis}

\subsection{Threats to Validity}
